The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-05 article.tex
Undo removal of removed message, undo addition of autogenerated files
upd refferences and grammar in intro

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this is a state detection system validation that allows agents to detect subversive or malfunctioning agents in their environment. The detection of such compromised agents can be used to create a trusted set within a group, providing a multi-node trust system. A TurtleBot running Robot Operating System (ROS) platform is used for implementation and performance is also evaluated in the Gazebo simulator.

@@

\section{Introduction}
With drones in land, air and sea coming into the growing consumer and private markets, the security involved in groups of these machines must be further studied. Robot security has landed headlines across a variety of commonly used devices, car hacking having a prominent impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles \cite{greenberg2015hackers}. As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. In a full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify various modules of an agent such as the static software, dynamic software, control system and communication of the agent.

@@

Once communication is secured, an adversary can distort the sensor data of an agent in order to lead it in a stray. An agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established usage envelope, a term coined here as a pre-computed state trajectory map. This map allows for a large variety of planning algorithms to be used. In light that there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

Redundant measurements in the system allow for an agents inside a trusted set to verify each other's locations. With and without feedback from others in the system, through the use of  several Kalman filters an agent is able to verify the positions of others relative to itself.

We now relate some work related to integrity, availability, and confidentiality, and further discuss the implementation technique used.

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as \cite{adi2009mechatronic} where a DNA clone resistant approach is taken throughout; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is part of a larger work which incorporates a HSE which is used to provide a unique hardware signature used to verify other parts of the system much like \cite{adi2009mechatronic}.

@@

The application of the KF to the task of robot localization has been studied intently \cite{Localization2003, Mohsin2014}. In \cite{Mohsin2014}, it is explained to be so popular for three main reasons. First, it is optimal under certain reasonable and common assumptions, second that it is recursive which is memory efficient, and finally that it relies only on having knowledge of noisy sensor data and not being able to measure certain state variables directly.

@@

\cite{Mo2010} and \cite{Yang2013} both demonstrate that KFs are susceptible to false data injection attacks, and that even with failure detectors a clever adversary can craft their attack to bypass these detectors. \cite{Bezzo_2014} and \cite{Mo2014} both attack this problem by adding extra steps into their KF algorithm. Both successfully show that the filter output can be shielded from the effects of the attack.

\subsubsection{Confidentiality: Secure Ad-Hoc Channel Communication}
There are various works that cover a communications for adhoc networks. \cite{vegh2014securing} uses an extension of the ElGamal algorithm in order to limit the access of agents in the network. In the event that an agent is compromised the information within the decrypted message remains protected through steganography, a method used for hiding information within a text \cite{adi2009mechatronic}. The implementation uses direct agent to agent communication and thus no hierarchy is used; no encrypted broadcast messages are sent and it seems unnecessary to encrypt the information further as it would lead to potential DOS attacks.

Another protocol introduced in \cite{chang2016provably} provides forward secrecy through registration, authentication and password changing involving communication between user, sensor and gateway nodes. A long term secret is used for the session and a change in password occurs once the connection is established; however, in a moving environment there may instances when only two nodes will be able to communicate at one time.

In the field of automobiles \cite{lyu2016pba} developed a protocol named PBA that is well guarded against high traffic and lossy wireless networks. Work in \cite{lyu2016pba} addresses DOS attack resistance and stores shortened MAC address signatures for memory consumption and rapid verification. \cite{lyu2016pba} takes a private public key pair approach which may be prone to further attacks as the base station could update their keys. Connectivity to the central station after the release is not taken to be necessary in this paper's approach.

\subsection{Distributed State Estimation}
As wireless networks become more and more omnipresent in our world, and given the increasing number and decreasing costs of mobile robots, the concept of a distributed state estimation system is very desirable. Given the rapid rise of these technologies though, the amount of research done into distributed systems is quite small compared to that for single robots. This was true years ago (\cite{Parker2000}), and is still true today.

@@

Most research into such distributed systems relies on the concept of cooperative positioning. That is, the robots coordinate their motions in order to use their sensors to determine the state of the other robots. Most often this involves one robot acting as a stationary landmark while the other robot moves. \cite{Kurazume1994}, \cite{Kurazume1996}, \cite{Kurazume1998}, and \cite{Kurazume2000} all explore the idea of cooperative positioning. This is a valuable and effective concept when working with a team of coordinated robots. However many systems will not allow for such close cooperation. For example, autonomous cars on a highway will not be able to start and stop for each other and still get to their destination on time. And in rush hour in a city the processing power needed to coordinate a plan for the thousands of cars on the road would be incredible.

Other work into distributed systems still makes the assumption of a cooperative team. \cite{Sanderson1997} and \cite{Roumeliotis2002} both demonstrate a system where a KF is implemented that estimates the state of multiple robots in a system. However these states are computed relative to each other, considering the network of robots to be essentially one large robot with different parts. Continuing the highway example, cars will be moving in and out of communication with each other as some enter the highway and others exit. Thus the group of robots will be constantly changing and evolving, a challenge not tackled by these works.

The previously mentioned works are all examples of a decentralized, rather than distributed KF problem. \cite{Olfati-Saber2005} makes clear the distinction between these two, saying:
\begin{quote}"...[decentralized] methods require a complete network with all-to-all links. This solution is not scalable for large-scale sensor networks... Thus, decentralized Kalman filtering and distributed Kalman filtering are two separate problems. In the latter one, each node only is allowed to communicate with its nieghobrs on a graph $G$ that is connected but rather sparse."
\end{quote}
\cite{Olfati-Saber2005} presents a solution to the distributed problem using consensus filters and multiple KFs. However this work still requires adaptation of the KFs and extra computation, which is something we try to avoid.

@@

In order to obtain behavior that is expected and not expected different types of planning have been introduced in literature. Complex environments can be made up of many possible paths which can be computed with strategies such as that of \cite{tallavajhula2016list}, where each iteration of path planning uses a more complex predictor. Each of these predictors' path can be used to build a map of states and corresponding behavior that an agent is able to perform.

Other planning algorithms use specialized planning based on a sub process task such as \cite{ahn2008robust}'s vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior, we will however demonstrate the concept through an avoidance task.

>>>>

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinate between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this is a state detection system validation allows agents to detect subversive or malfunctioning agents in their environment. The detection of such compromised agents can be used to create a \textit{trusted set} within a group, providing a multi-node trust system. A TurtleBot running Robot Operating System (ROS) platform is used for implementation and performance is also evaluated in the Gazebo simulator.

@@

\section{Introduction}
With drones in land, air and sea coming into the growing consumer and private markets, the security involved in groups of these machines must be studied further. Robot security has landed headlines across a variety of commonly used devices, car hacking having a prominent impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles \cite{greenberg2015hackers}. As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. In a full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify various modules of an agent such as the static software, dynamic software, control system and communication between agents.

@@

Once communication is secured, an adversary can distort the sensor data of an agent in order to lead it in a stray. An agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established \textit{usage envelope}, a pre-computed state trajectory map. This map allows for a large variety of planning algorithms to be used. In light that there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

Redundant measurements in the system allow for an agents inside a trusted set to verify each other's locations. With and without feedback from others in the system, an agent is able to verify the positions of others relative to itself through the use of several Kalman filters.

We now relate some work related to integrity, availability, and confidentiality, and further discuss the implementation technique used. We then demonstrate our experiments and gather a conclusion from the results and motivation of the paper.

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as adi et al where a DNA clone resistant approach is taken throughout\cite{adi2009mechatronic}; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is the HSE which is used to verify other parts of the system much like adi et al\cite{adi2009mechatronic}.

@@

The application of the KF to the task of robot localization has been studied intently \cite{Localization2003, Mohsin2014}. In Mohsin et al, it is explained to be so popular for three main reasons\cite{Mohsin2014}. First, it is optimal under certain reasonable and common assumptions, second that it is recursive which is memory efficient, and finally that it relies only on having knowledge of noisy sensor data and not being able to measure certain state variables directly.

@@

Mo et al and Yang et al both demonstrate that KFs are susceptible to false data injection attacks, and that even with failure detectors a clever adversary can craft their attack to bypass these detectors \cite{Mo2010}\cite{Yang2013}. Bezzo et al and Mo et al both attack this problem by adding extra steps into their KF algorithm\cite{Bezzo_2014}\cite{Mo2014}. Both successfully show that the filter output can be shielded from the effects of the attack.

\subsubsection{Confidentiality: Secure Ad-Hoc Channel Communication}
There are various works that cover a communications for adhoc networks. Vegh et al uses an extension of the ElGamal algorithm in order to limit the access of agents in the network\cite{vegh2014securing}. In the event that an agent is compromised the information within the decrypted message remains protected through steganography, a method used for hiding information within a text \cite{adi2009mechatronic}. The implementation uses direct agent to agent communication and thus no hierarchy is used; no encrypted broadcast messages are sent and it seems unnecessary to encrypt the information further as it would lead to potential DOS attacks.

Another protocol introduced in Chang et al provides forward secrecy through registration, authentication and password changing involving communication between user, sensor and gateway nodes \cite{chang2016provably}. A long term secret is used for the session and a change in password occurs once the connection is established; however, in a moving environment there may instances when only two nodes will be able to communicate at one time.

In the field of automobiles Lyu et al developed a protocol named PBA that is well guarded against high traffic and lossy wireless networks\cite{lyu2016pba}. The same work addresses DOS attack resistance and stores shortened MAC address signatures for memory consumption and rapid verification \cite{lyu2016pba}. Lyu et al takes a private public key pair approach which may be prone to further attacks as the base station could update their keys \cite{lyu2016pba}. Connectivity to the central station after the release is not taken to be necessary in this paper's approach.

\subsection{Distributed State Estimation}
As wireless networks become more and more omnipresent in our world, and given the increasing number and decreasing costs of mobile robots, the concept of a distributed state estimation system is very desirable. Given the rapid rise of these technologies though, the amount of research done into distributed systems is quite small compared to that for single robots. This was true years ago , and is still true today\cite{Parker2000}.

@@

Most research into such distributed systems relies on the concept of cooperative positioning. That is, the robots coordinate their motions in order to use their sensors to determine the state of the other robots. Most often this involves one robot acting as a stationary landmark while the other robot moves. Kurazume et al's works all explore the idea of cooperative positioning\cite{Kurazume1994}\cite{Kurazume1996}\cite{Kurazume1998} \cite{Kurazume2000}. This is a valuable and effective concept when working with a team of coordinated robots. However many systems will not allow for such close cooperation. For example, autonomous cars on a highway will not be able to start and stop for each other and still get to their destination on time. And in rush hour in a city the processing power needed to coordinate a plan for the thousands of cars on the road would be incredible.

Other work into distributed systems still makes the assumption of a cooperative team. Sanderson et al and Roumeliotis et al both demonstrate a system where a KF is implemented that estimates the state of multiple robots in a system \cite{Sanderson1997}\cite{Roumeliotis2002}. However these states are computed relative to each other, considering the network of robots to be essentially one large robot with different parts. Continuing the highway example, cars will be moving in and out of communication with each other as some enter the highway and others exit. Thus the group of robots will be constantly changing and evolving, a challenge not tackled by these works.

The previously mentioned works are all examples of a decentralized, rather than distributed KF problem. Olfati-Saber et al makes clear the distinction between these two, saying \cite{Olfati-Saber2005}:
\begin{quote}"...[decentralized] methods require a complete network with all-to-all links. This solution is not scalable for large-scale sensor networks... Thus, decentralized Kalman filtering and distributed Kalman filtering are two separate problems. In the latter one, each node only is allowed to communicate with its nieghobrs on a graph $G$ that is connected but rather sparse."
\end{quote}
Olfati-Saber et al presents a solution to the distributed problem using consensus filters and multiple KFs\cite{Olfati-Saber2005}. However this work still requires adaptation of the KFs and extra computation, which is something we try to avoid.

@@

In order to obtain behavior that is expected and not expected different types of planning have been introduced in literature. Complex environments can be made up of many possible paths which can be computed with strategies such as that of Tallavajhula et al, where each iteration of path planning uses a more complex predictor\cite{tallavajhula2016list}. Each of these predictors' path can be used to build a map of states and corresponding behavior that an agent is able to perform.

Other planning algorithms use specialized planning based on a sub process task such as ahn et al's vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects\cite{ahn2008robust}. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior, we will however demonstrate the concept through an avoidance task.
